%-------------------------
% Resume in Latex
% Author : Vaishanth
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}%\setmainfont{Times New Roman}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}

\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Color hyperlinks instead of repeating \color{blue} per-link
\hypersetup{colorlinks=true, urlcolor=cvblue, linkcolor=cvblue}
% Separator between header contact links
\newcommand{\sep}{~{\small$\cdot$}~}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% \usepackage[T1]{fontenc}
% \usepackage[T1]{fontenc}
% \usepackage{cochineal}
% \usepackage{fourier}

% \usepackage{fontspec}
% \usepackage{polyglossia}
% \setmainlanguage{german}
% \setmainfont{Times New Roman}

% serif
\usepackage{CormorantGaramond}
\usepackage{charter}

% \pagestyle{fancy}
% \fancyhf{}  % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}
\urlstyle{same}

\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      \textit{\large#3} & \textit{\small #4} \\
      
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSingleSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.1in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------\usepackage{fontspec}
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
%----------HEADING----------


\begin{center}
    {\huge\bfseries Beckett Frey} \\ \vspace{4pt}
    \href{https://github.com/stars/BeckettFrey/lists/portfolio}{Portfolio} \sep
    \href{https://github.com/beckettfrey}{GitHub} \sep
    \href{https://linkedin.com/in/beckettfrey}{LinkedIn} \sep
    \href{mailto:hello@beckettfrey.com}{Email}
    \vspace{-7pt}
\end{center}

%-----------EDUCATION-----------
\section{\color{airforceblue}EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {UW Milwaukee}{Milwaukee, WI, USA}
      {B.S. Computer Science}{January 2023 - May 2025}
    % \vspace{-4pt}
    %  \resumeSubheading
    %   {University 2}{Location, State, USA}
    %   {Degree and Specialization}{Month Year - Month Year}
  \resumeSubHeadingListEnd
  \vspace{-10pt}

%-----------PROGRAMMING SKILLS-----------
\section{\color{airforceblue}TECHNICAL SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{\normalsize{Programming Languages:}}{ \normalsize{Python, TypeScript, Bash, SQL, R}} \\
      \vspace{1.2pt}
      
     \textbf{\normalsize{Tools and Frameworks:}}{ \normalsize{Django, React, PyQt6, LangGraph, Node.js}} \\
      \vspace{1.2pt}

     \textbf{\normalsize{Cloud and Infra:}}{ \normalsize{GitHub Actions, Docker, Modal, AWS}} \\
      \vspace{1.2pt}
    
      \textbf{\normalsize{Speech and Audio ML:}}{ \normalsize{Forced Alignment, Whisper, Pyannote}} \\
      \vspace{1.2pt}

     \textbf{\normalsize{Computer Vision:}}{ \normalsize{Object Detection (YOLO), Synthetic Data, mAP Evaluation}} \\
      \vspace{1.2pt}
     % copy and paste above textbf block to add more 
     }}
 \end{itemize}
 \vspace{-16pt}
 
 %-----------EXPERIENCE-----------
\section{\color{airforceblue}WORK EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer (Volunteer)}{} 
      {Environmental Data \& Governance Initiative, Remote, USA}{January 2026 - Present}
      \resumeItemListStart
            \resumeItem{\normalsize{Resolve bugs and deliver features for the web-monitoring project in response to analyst feedback.}}
            \resumeItem{\normalsize{Explore Docker Hardened Images to improve container security.}}
            \resumeItem{\normalsize{Improve CI with ruff and git hooks to gate low-quality open-source contributions before review.}}
            \resumeItem{\normalsize{Collaborate with a team of volunteers across the country for environmental justice.}}
      \resumeItemListEnd

    \resumeSubheading
      {Research Intern}{} 
      {Waisman Center, WI, USA}{September 2025 - Present}
      \resumeItemListStart
            \resumeItem{\normalsize{Build pipelines with GitHub actions and docker across multiple code repositories to protect researchers time.}}
            \resumeItem{\normalsize{Develop Python and Bash scripts to automate repetitive parts of the data collection pipeline.}}  
            \resumeItem{\normalsize{Collaborate across labs to support the ongoing development of legacy django Infrastructure, focusing on modernization and knowledge continuity.}}
            \resumeItem{\normalsize{Code and market a cross-platform desktop application for phonetic research, helping onboard less technical researchers and automating metadata tracking for reproducibility.}}
            \resumeItem{\normalsize{Support researchers applying machine learning to automate pronunciation assessment for children with speech sound disorders.}}
      \resumeItemListEnd

    \resumeSubheading
      {Junior ML Engineer}{} 
      {Hyperchess.ai, Remote, USA}{December 2024 - September 2025}
      \resumeItemListStart
            \resumeItem{\normalsize{Built a synthetic data pipeline and a 25-model YOLO mixture-of-experts for piece detection, reaching 99\% mAP@0.5.}}
            \resumeItem{\normalsize{Deployed inference workloads with Modal serverless GPU, drastically improving the speed of iteration.}}
      \resumeItemListEnd

    % copy and paste above resumeSubheading block to add more 
  \resumeSubHeadingListEnd
\vspace{-12pt}


 %-----------PROJECTS-----------
\section{\color{airforceblue}PROJECTS}
    \resumeItemListStart
        \vspace{0.5pt}

        \resumeItem{\normalsize{\textbf{Phonetic Research Application}, Cross-platform desktop app that unifies AI/ML tools (MFA, Wav2TextGrid, Faster-Whisper, PyPLLRComputer) behind one interface, letting Speech Language Pathology researchers build and run phonetic analysis pipelines in one place.}  \href{https://voxkit-web.vercel.app/}{Try it!}}
        \vspace{-5pt}

        \resumeItem{\normalsize{\textbf{Data Security Tooling}, Published PyPI tool that scans git repositories for PHI and other identifier patterns. Used to safely open-source several lab repos and caught one real PHI exposure in legacy code.}  \href{https://pypi.org/project/shred-guard/}{Try it!}}
        \vspace{-5pt}

        \resumeItem{\normalsize{\textbf{AI Document Generation}, Divides document generation into per-placeholder tasks queued by batch. Supports context injection and an enforced length range per task.} \href{https://github.com/beckettfrey/doc-weaver-agent}{GitHub}}
        \vspace{-5pt}

        \resumeItem{\normalsize{\textbf{Multiplayer Chess API}, Chess backend in TypeScript/Node.js using WebSockets to sync game state and lobbies across clients.} \href{https://github.com/beckettfrey/ChessLink}{GitHub}}

        % copy and paste above resumeItem block to add more 
        
    \resumeItemListEnd  
   
 \vspace{-12pt}
%

%-----------Publications---------------
% \section{\color{airforceblue}PUBLICATIONS}
    
%   \resumeItemListStart
%     \resumeItem{\normalsize{Add Publication details here}}\href{[url link to publication]}{\color{blue}\underline{Link}}
%     \vspace{-5pt}
    
%     \resumeItem{\normalsize{Add Publication details here}}\href{[url link to publication]}{\color{blue}\underline{Link}}
%     \vspace{-5pt}

%     % copy and paste above resumeItem block to add more 
    
%   \resumeItemListEnd 
      
% \vspace{-8pt}

%-----------EXTRACURRICULAR---------------
\section{\color{airforceblue}EXTRACURRICULAR ACTIVITIES}
    
      \resumeItemListStart

        \resumeItem{\normalsize{\textbf{Open Source Contributor}, Github -} {Ongoing}}    
        \vspace{-5pt}

        \resumeItem{\normalsize{\textbf{Inpatient Unit Support}, UW Health -} {Ongoing}}
        \vspace{-5pt}
        
        \resumeItem{\normalsize{\textbf{Bartender}, Ralley on the Runway -} {September 2024}} 
        \vspace{-5pt}

        \resumeItem{\normalsize{\textbf{Triathlete}, IRONMAN Wisconsin -} {September 2023}}    
        \vspace{-5pt}
        
        % copy and paste above resumeItem block to add more 
      \resumeItemListEnd 
      
\vspace{-12pt}

\end{document}